A distance metric between histograms through the the Kolmogorov-Smirnov test statistic: specification, measures reference and example uses

### 2015-10-31 paper.tex
pequenas melhoras

\begin{abstract}
This document presents reference values for a distance metric
derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
Each measure of $D_{F,F'}$ is a distance between two histograms,
which is normalized by the number of observations in each sample
to yield the $c$ statistic, which can be mapped to p-values, i.e. values for which 
higher levels of significance $\alpha>c(\alpha)$ implies the rejection of the null hypothesis.
Benchmarks for the implementation are delivered by comparing samples from known distributions.
Pattern examples in real data enables further
insight in the robustness and power of $c$.
\end{abstract}

@@

Hight values of $c$ favor rejecting the null hypothesis.
For example, if the significance level is $\alpha=0.01$,
then $c$ greater than $1.7$
implies the rejection of the null hypothesis and
suggests that $F$ and $F'$
are outcomes of different distributions.
Of core importance in this study is to regard the $c$ statistic
as a measure of distance between both distributions~\cite{kolm}.
The main contribution of the following sections is the
explicit display of reference values of $c$
from which one might derive knowledge from
measures or even from a single value of $c$.

@@

\subsection{Document outline}
Section~\ref{sec:simulations} exposes reference values drawn from simulations.
Section~\ref{sec:empirical} exemplifies the use of such reference values
to make sense of phenomena.
Section~\ref{sec:conc} holds final remarks.
Software and data specification are given in Appendix~\ref{ap:soft}.

\section{References through simulations}\label{sec:simulations}
On every case, values of $c$ are given for simulations involving
at least normal, uniform, Weibull and power function distributions.
The rendering of this article is automated to ease changes in
the settings with which the results are reported.
\input{aux/preambule1}

\subsection{When the null hypothesis is true}
If the null hypothesis is true, than the number
of rejections of the null hypothesis (that is: $c>c(\alpha)$)
in $N_c$ comparisons should not exceed $\alpha N_c$.
To verify this, let $C=\{c_i\}$ be a set of $c$ measures,
and $C(\alpha)=\{c : c>c(\alpha)\}$.
Be $|C(\alpha)|$ the cardinality of $C(\alpha)$,
i.e. the number of comparisons in which the two-sample Kolmogorov-Smirnov
test rejects the null hypothesis for a given $\alpha$.
This section reports that
$|C(\alpha)|$ very rarely exceeds $\alpha N_c$,
for all probability distributions and settings.
Also important are that
$c>c(\alpha)$ in many cases
and that the tabulated $\alpha$ values
are also good estimates of the upper limit
of the frequency of such an event.

>>>>

\begin{abstract}
This document presents reference values for a distance metric
derived from the Kolmogorov-Smirnov test statistic $D_{F,F'}$.
Each measure of $D_{F,F'}$ is a distance between two histograms,
which is normalized by the number of observations in each sample
to yield the $c$ statistic, which can be mapped to p-values, i.e. values for which 
high enough levels of significance $\alpha$ implies the rejection of the null hypothesis.
Benchmarks for the implementation are delivered by comparing samples from known distributions.
Pattern examples in real data enables further
insight in the robustness and power of $c$.
\end{abstract}

@@

High values of $c$ favor rejecting the null hypothesis.
For example, if the significance level is $\alpha=0.01$,
then $c$ greater than $1.7$
implies the rejection of the null hypothesis and
suggests that $F$ and $F'$
are outcomes of different distributions.
Of core importance in this study is to regard the $c$ statistic
as a measure of distance between both distributions~\cite{kolm}.
The main contribution of the following sections is the
explicit display of reference values of $c$
from which one might derive knowledge from
measures or even from a single value of $c$.

@@

\subsection{Document outline}
Section~\ref{sec:simulations} exposes reference values drawn from simulations.
Section~\ref{sec:empirical} exemplifies the use of the $c$ statistic
to make sense of phenomena.
Section~\ref{sec:conc} holds final remarks with directions to
software and data.

\section{References through simulations}\label{sec:simulations}
Values of $c$ are given for simulations involving
normal, uniform, Weibull and power function distributions.
The rendering of this article is automated to ease changes in
the settings with which the results are reported.
\input{aux/preambule1}

\subsection{When the null hypothesis is true}
If the null hypothesis is true, the number
of rejections of the null hypothesis ($c>c(\alpha)$)
in $N_c$ comparisons should not exceed $\alpha N_c$.
To verify this, let $C=\{c_i\}$ be a set of $c$ measures,
and $C(\alpha)=\{c : c>c(\alpha)\}$.
Be $|C(\alpha)|$ the cardinality of $C(\alpha)$,
i.e. the number of comparisons in which the two-sample Kolmogorov-Smirnov
test rejects the null hypothesis for a given $\alpha$.
This section reports that
$|C(\alpha)|$ very rarely exceeds $\alpha N_c$,
for all probability distributions and settings.
Also important are that
$c>c(\alpha)$ in many cases
and that the tabulated $\alpha$ values
are also good estimates of the upper limit
of the frequency of such an event.
